---
title: "Data Management of DEPP cohort Evalaide - Create classes"
author:
  - Pauline Martinot [UNICOG, NeuroSpin]
  - Bénédicte Colnet [Inria, Paris-Saclay]
date: "July 2023"
output:
  pdf_document:
    toc: yes
  html_document:
    number_sections: no
    toc: yes
    toc_depth: 2
abstract: | 
  This notebook takes as an entry the output from notebook 2_ and create classes data frame with only class-related covariates.
---

```{r}

knitr::opts_chunk$set(echo = TRUE)
# Seed because application of PCA on a random sample

set.seed(123)

# Parameters to set before launch of the pipeline

IMPUTED = "imputed" # "imputed" "non-imputed"
NAOMIT = "False" # "False"
ANNEE_COHORTE = "2018" #"2019" #"2020" #"2021"

# Libraries

library(dplyr)
library(tidyverse)
library(tibble)
library(reshape2)

```

# Load data

```{r}
# Data

if(IMPUTED == "non-imputed"){
  if(NAOMIT == "True"){
load(paste0("~/Data/cohort_", ANNEE_COHORTE, "_", IMPUTED, "_after_2_composite_covariate_naomit_True.RData"))
  } else if (NAOMIT == "False"){
load(paste0("~/Data/cohort_", ANNEE_COHORTE, "_", IMPUTED, "_after_2_composite_covariate_naomit_False.RData"))
    }
}

if(IMPUTED == "imputed"){
load(paste0("~/Data/cohort_", ANNEE_COHORTE, "_", IMPUTED, "_after_2_composite_covariate.RData"))
} 

```

# SELECT only classes big enough > SEUIL_INF_CLASS and not too big < SEUIL_SUP_CLASS

```{r}

SEUIL_INF_CLASS = 5

dim(data_depp)

data_depp <- data_depp[data_depp$Taille_Classe < SEUIL_SUP_CLASS & data_depp$Taille_Classe > SEUIL_INF_CLASS,]

dim(data_depp)

```


## Intermediate classes table

```{r}
# Extract all classes ID
all_classes_ids <- unique(data_depp$ID_etab_class)

# Instantiate
classes <- data_depp[, c("ID_etab_class", "Categ_Etab_CP", "Taille_Classe", "Taille_Classe_Cat", "Taille_Ecole", "IPS_Etab_CP")] %>%
  group_by(ID_etab_class, Categ_Etab_CP, Taille_Classe, Taille_Classe_Cat, Taille_Ecole)
classes <- unique(classes)
# Sanity check
nrow(classes) ==  length(all_classes_ids)
```


```{r}
dim(classes)
```

# Creating Nb of boys and girls per class

selecting min of 30% of girls and boys per class

```{r}

# building a variable for number of boys per class

nmixity <- data_depp[, c("ID_etab_class", "Sexe_Num")]
nmixity$Sexe_Num <- ifelse(nmixity$Sexe_Num == -0.5, 0, 1)
nmixity <- nmixity %>%
  group_by(ID_etab_class) %>%
  summarise(n_boy = sum(Sexe_Num))

classes <- merge(classes, nmixity[ , c("ID_etab_class", "n_boy")], by = "ID_etab_class")

# building a variable for number of girls per class

nmixity <- data_depp[, c("ID_etab_class", "Sexe_Num")]
nmixity$Sexe_Num <- ifelse(nmixity$Sexe_Num == -0.5, 0, 1)
nmixity <- nmixity %>%
  group_by(ID_etab_class) %>%
  summarise(n_girls = sum(Sexe_Num == 0))

classes <- merge(classes, nmixity[ , c("ID_etab_class", "n_girls")], by = "ID_etab_class")

rm(nmixity)

# classes <- classes[classes$n_boy > 1 & classes$n_girls > 1, ] # selecting min 2 boys and 2 girls per class

classes$n_boy   <- as.numeric(classes$n_boy)
classes$n_girls <- as.numeric(classes$n_girls)

Classes_singlesex_boys <- classes[classes$n_girls == 0, ]
Classes_singlesex_girls <- classes[classes$n_boy == 0, ]

sum(Classes_singlesex_boys$Taille_Classe)
sum(Classes_singlesex_girls$Taille_Classe)

```

```{r}

ggplot(classes, aes(x = n_boy)) +
  geom_histogram() +
  theme_bw()

ggplot(classes, aes(x = n_girls)) +
  geom_histogram() +
  theme_bw()

```

# Boy_proportion = Mixity : Create variable for class mixity

```{r}

# compute mixity

mixity <- data_depp[, c("ID_etab_class", "Sexe_Num")]
mixity$Sexe_Num <- ifelse(mixity$Sexe_Num == -0.5, 0, 1)
mixity <- mixity %>%
  group_by(ID_etab_class) %>%
  summarise(boy_proportion = sum(Sexe_Num)/n())

# merge mixity with classes

classes <- merge(classes, mixity [ , c("ID_etab_class", "boy_proportion")], by = "ID_etab_class")
classes$boy_proportion <- round(classes$boy_proportion,2)

# clean memory

rm(mixity)

# check number of new dimension

dim(classes)

# plot

ggplot(classes, aes(x = boy_proportion)) +
  geom_histogram() +
  theme_bw()

```


# Mean per class = Create average values for all grades and rank per class = "_mean_per_class"

Create this for the 44 tests, the 44 tests in percentage, the 44 tests in rank, the 6 synthetic covariates_P, and also the 6 covariates in rank. This ends with 144 additional columns.

```{r}
  
grades_to_average <- c("Age_CP", notes, notes_P, 
                       "T1_Math", "T2_Math", "T3_Math",
                       "T1_Language", "T2_Language", "T3_Language",
                       "T1_Math_Rank", "T2_Math_Rank", "T3_Math_Rank",
                       "T1_Lang_Rank", "T2_Lang_Rank", "T3_Lang_Rank")

reversed_table <- melt(data_depp[, c(grades_to_average,"ID_etab_class")], id = c("ID_etab_class"))

average <- dcast(reversed_table, ID_etab_class ~ variable, mean)

classes <- merge(average, classes, by = "ID_etab_class")

rm(reversed_table)

# check dimension

dim(classes)

# rename
names(classes)[names(classes) %in% grades_to_average] <- paste0(grades_to_average, "_mean_per_class")

# clean workspace
rm(average)
rm(grades_to_average)

colnames(classes)



```


```{r}
# # sanity checks for 2019
mean(data_depp[data_depp$ID_etab_class == "001839365f87e7ab_27c4180baadb", "T1_Math"]) == classes[classes$ID_etab_class == "001839365f87e7ab_27c4180baadb", "T1_Math_mean_per_class"]

# # sanity checks for 2018
mean(data_depp[data_depp$ID_etab_class == "0000993518d99f92_2114bfa81bad", "T1_Math"]) == classes[classes$ID_etab_class == "0000993518d99f92_2114bfa81bad", "T1_Math_mean_per_class"]
```



# First of class in the "class data frame" : if the top first child(ren) in math of a class is/are boy(s) or girl(s) : Create a variable to indicate this 

For example in cohort 2018, class id "000dac02c20c7437_c6f54135e39e" as two girls being first with grade 87 in T1_Math, this will be indicated with -1 in the column "sum_Sexe_num_first_T1_Math" in the data frame classes.

```{r}

synthetic_grades <- c("T1_Math", "T2_Math", "T3_Math",
                      "T1_Language", "T2_Language", "T3_Language")

for (grade in synthetic_grades){
  
  # create sum of gender of the top children per class and store in temp
  temp <- data_depp[, c("ID_etab_class", "Sexe_Num", grade)] %>%
    # mutate_at(all_of(grade) , funs(round(., 0))) %>% 
    group_by(ID_etab_class) %>%
    top_n(1, !!as.name(grade)) %>%
    #mutate(count_first_T1_Math = n()) %>% # if wanna count number of first ex-aequo children per class
    group_by(!!as.name(grade), ID_etab_class) %>%
    mutate(mean = mean(Sexe_Num))
  
  # kepp only relevant columns and name it accordingly
  temp <- unique(temp[, c("mean", "ID_etab_class")])
  names(temp)[names(temp) == "mean"] <- paste0("First_mean_sexe_in_", grade)
  
  # create column
  classes <- merge(classes, temp, by = "ID_etab_class")
}

# clean memory
rm(temp)

# check number of dimensions
dim(classes)


synthetic_grades <- c("T1_Math_Rank", "T2_Math_Rank", "T3_Math_Rank", 
                      "T1_Lang_Rank", "T2_Lang_Rank", "T3_Lang_Rank")

for (grade in synthetic_grades){
  
  # create sum of gender of the top children per class and store in temp
  temp <- data_depp[, c("ID_etab_class", "Sexe_Num", grade)] %>%
    # mutate_at(all_of(grade), funs(round(., 0))) %>%
    group_by(ID_etab_class) %>%
    top_n(1, !!as.name(grade)) %>%
    #mutate(count_first_T1_Math = n()) %>% # if wanna count number of first ex-aequo children per class
    group_by(!!as.name(grade), ID_etab_class) %>%
    mutate(mean = mean(Sexe_Num))
  
  # kepp only relevant columns and name it accordingly
  temp <- unique(temp[, c("mean", "ID_etab_class")])
  names(temp)[names(temp) == "mean"] <- paste0("First_mean_sexe_in_", grade)
  
  # create column
  classes <- merge(classes, temp, by = "ID_etab_class")
}

# clean memory
rm(temp)

# check number of dimensions
dim(classes)


```

### Improving First mean sexe in math and language

instead of having 2 or 3 first of class with different or similar genders, we implemented a mean of their gender and allocated the positive values to "more boys were first of class", a negative value to "more girls were first of class" and a neutral value to "mixed"

```{r}
# First Math

table(classes$First_mean_sexe_in_T1_Math)

classes$First_sexe_in_T1_Math <- case_when(classes$First_mean_sexe_in_T1_Math > 0 ~ 0.5,
                                       classes$First_mean_sexe_in_T1_Math < 0 ~ -0.5,
                                       classes$First_mean_sexe_in_T1_Math ==  0 ~ 0)

summary(classes$First_sexe_in_T1_Math)

# First Language 

table(classes$First_mean_sexe_in_T1_Language)

classes$First_sexe_in_T1_Language <- case_when(classes$First_mean_sexe_in_T1_Language > 0 ~ 0.5,
                                       classes$First_mean_sexe_in_T1_Language < 0 ~ -0.5,
                                       classes$First_mean_sexe_in_T1_Language ==  0 ~ 0)

summary(classes$First_sexe_in_T1_Language)

```


# Create mean of a class for girls and boys per class.

This adds 2 gender times 6 synthetic grades columns in percent and 6 synthetic columns in ranks.

```{r}

synthetic_grades <- c("Age_CP", "T1_Math", "T2_Math", "T3_Math",
                      "T1_Language", "T2_Language", "T3_Language")

for (grade in synthetic_grades){
  for (gender in c("Boys", "Girls")){
    temp <- data_depp[data_depp$Sexe == gender, c("ID_etab_class", grade)] %>%
      group_by(ID_etab_class) %>%
      summarise(mean = mean(!!as.name(grade)))

  # Name it accordingly
  names(temp)[names(temp) == "mean"] <- paste0("mean_", grade, "_", gender)

  # create column
  classes <- merge(temp, classes, by = "ID_etab_class", all.y = T)
  }
}

# clean memory
rm(temp, synthetic_grades)

# check dimension
dim(classes)




synthetic_grades <- c("T1_Lang_Rank", "T2_Lang_Rank", "T3_Lang_Rank")

for (grade in synthetic_grades){
  for (gender in c("Boys", "Girls")){
    temp <- data_depp[data_depp$Sexe == gender, c("ID_etab_class", grade)] %>%
      group_by(ID_etab_class) %>%
      summarise(mean = mean(!!as.name(grade)))

  # Name it accordingly
  names(temp)[names(temp) == "mean"] <- paste0("mean_", grade, "_", gender)

  # create column
  classes <- merge(temp, classes, by = "ID_etab_class", all.y = T)
  }
}

rm(temp, synthetic_grades)



synthetic_grades <- c("T1_Math_Rank", "T2_Math_Rank", "T3_Math_Rank")

for (grade in synthetic_grades){
  for (gender in c("Boys", "Girls")){
    temp <- data_depp[data_depp$Sexe == gender, c("ID_etab_class", grade)] %>%
      group_by(ID_etab_class) %>%
      summarise(mean = mean(!!as.name(grade)))

  # Name it accordingly
  names(temp)[names(temp) == "mean"] <- paste0("mean_", grade, "_", gender)

  # create column
  classes <- merge(temp, classes, by = "ID_etab_class", all.y = T)
  }
}

rm(temp, synthetic_grades)


```

# Create difference in mean for girls and boy

For example D_T1_Math is the difference of mean of boys - girls
This creates 6 additional columns.

For example D_T1_Math_Rank is the difference of mean_Rank of boys - girls
This creates 6 additional columns.

### D_T1_Math

```{r}

synthetic_grades <- c("T1_Math", "T2_Math", "T3_Math",
                      "T1_Language", "T2_Language", "T3_Language")

for (grade in synthetic_grades){
  
  classes[, paste0("D_", grade)] <- classes[, paste0("mean_", grade, "_Boys")] - classes[, paste0("mean_", grade, "_Girls")]
    
}

rm(synthetic_grades)

```

### D_T1_Math_Rank

```{r}

synthetic_grades <- c("T1_Lang_Rank", "T2_Lang_Rank", "T3_Lang_Rank", "T1_Math_Rank", "T2_Math_Rank", "T3_Math_Rank")

for (grade in synthetic_grades){
  
  classes[, paste0("D_", grade)] <- classes[, paste0("mean_", grade, "_Boys")] - classes[, paste0("mean_", grade, "_Girls")]
    
}

rm(synthetic_grades)


```




# Create mean of a class for girls and boys **without** the first children per class.

This adds 2 gender times 6 synthetic grades columns in percent.
This adds 2 gender times 6 synthetic grades columns in ranks.

### first in Math T1

```{r}


synthetic_grades <- c("T1_Math", "T2_Math", "T3_Math",
                      "T1_Language", "T2_Language", "T3_Language")

for (grade in synthetic_grades){
  for (gender in c("Boys", "Girls")){
    temp <- data_depp[!data_depp[, paste0("first_in_", grade)] & data_depp$Sexe == gender,
                      c("ID_etab_class", grade)] %>%
  group_by(ID_etab_class) %>%
  summarise(mean = mean(!!as.name(grade)))

  # Name it accordingly
  names(temp)[names(temp) == "mean"] <- paste0("mean_", grade, "_", gender, "_wo_first")

  # create column
  classes <- merge(temp, classes, by = "ID_etab_class", all.y = T)
  }

}
# clean memory
rm(temp, synthetic_grades)

# check dimension
dim(classes)

######

synthetic_grades <- c("T1_Math_Rank", "T2_Math_Rank", "T3_Math_Rank",
                      "T1_Lang_Rank", "T2_Lang_Rank", "T3_Lang_Rank")

for (grade in synthetic_grades){
  for (gender in c("Boys", "Girls")){
    temp <- data_depp[!data_depp[, paste0("first_in_", grade)] & data_depp$Sexe == gender,
                      c("ID_etab_class", grade)] %>%
  group_by(ID_etab_class) %>%
  summarise(mean = mean(!!as.name(grade)))

  # Name it accordingly
  names(temp)[names(temp) == "mean"] <- paste0("mean_", grade, "_", gender, "_wo_first")

  # create column
  classes <- merge(temp, classes, by = "ID_etab_class", all.y = T)
  }
}

# clean memory
rm(temp, synthetic_grades)

# check dimension
dim(classes)


```

# Create difference in mean for girls and boy without first : D_T1_Math_wo_first

D_T1_Math_wo_first is the difference of mean of boys - girls
This creates 6 additional columns.

```{r}

synthetic_grades <- c("T1_Math", "T2_Math", "T3_Math",
                      "T1_Language", "T2_Language", "T3_Language")

for (grade in synthetic_grades){
  classes[, paste0("D_", grade, "_wo_first")] <- classes[, paste0("mean_", grade, "_Boys_wo_first")] - classes[, paste0("mean_", grade, "_Girls_wo_first")]

}

rm(synthetic_grades)

######

synthetic_grades <- c("T1_Math_Rank", "T2_Math_Rank", "T3_Math_Rank",
                      "T1_Lang_Rank", "T2_Lang_Rank", "T3_Lang_Rank")

for (grade in synthetic_grades){
  classes[, paste0("D_", grade, "_wo_first")] <- classes[, paste0("mean_", grade, "_Boys_wo_first")] - classes[, paste0("mean_", grade, "_Girls_wo_first")]

}

rm(synthetic_grades)

plot(classes$boy_proportion, classes$D_T1_Math_Rank_wo_first)

```
# Remove

```{r}

rm(all_classes_ids, gender, grade)

```


# Select variables we want to keep

```{r}

if(ANNEE_COHORTE == 2020){
drop <- c("sd", "test_abnormalities_Lang_T1", "test_abnormalities_Lang_T2", "test_abnormalities_Math_T1", 
          "test_abnormalities_Math_T2", "test_abnormalities_T1", "test_abnormalities_T2", "totally_ab",
          "class_size_abnormalities", "age_abnormality" , "CodeClasseMi","CodeEtablissementMi", "strate_Mi",
          "ips_Mi")

data_depp = data_depp[ , !(names(data_depp) %in% drop )]

}

```

# SAVE Selections

Selected classes are from 6 to 27 and selection of classes with min 2 boys and 2 girls are for
- classes
- joined
- joined_n 
- joined30
- joined30_n

But not for data_depp : no selection 

# SAVE classes

```{r}

# Here classes contain at least 6 and maximum 27 children per class

if(IMPUTED == "non-imputed"){
  if(NAOMIT == "True"){
save(classes, file = paste0("~/Data/cohort_",  ANNEE_COHORTE, "_", IMPUTED, "_classes_naomit_True.RData"))
  } else if (NAOMIT == "False"){
save(classes, file = paste0("~/Data/cohort_",  ANNEE_COHORTE, "_", IMPUTED, "_classes_naomit_False.RData"))
    }
}

if(IMPUTED == "imputed"){
save(classes, file = paste0("~/Data/cohort_", ANNEE_COHORTE, "_", IMPUTED, "_classes.RData"))
}

```


# SAVE data_depp

- data_depp excluded classes < 5 and classes > 27

```{r}

# Here data_depp contains at least 6 and maximum 27 children per class


if(IMPUTED == "non-imputed"){
  if(NAOMIT == "True"){
save(data_depp, file = paste0("~/Data/cohort_",  ANNEE_COHORTE, "_", IMPUTED, "_data_depp_naomit_True.RData"))
  } else if (NAOMIT == "False"){
save(data_depp, file = paste0("~/Data/cohort_",  ANNEE_COHORTE, "_", IMPUTED, "_data_depp_naomit_False.RData"))
    }
}

if(IMPUTED == "imputed"){
save(data_depp, file = paste0("~/Data/cohort_", ANNEE_COHORTE, "_", IMPUTED, "_data_depp.RData"))
}

```

# SAVE joined

```{r}
# remove duplicated columns to avoid .x and .y columns
dim(data_depp)
data_depp <- subset(data_depp, select = -c(Categ_Etab_CP, Taille_Classe, Taille_Classe_Cat, Taille_Ecole, IPS_Etab_CP))
dim(data_depp)

# merge
joined <- merge(classes, data_depp, by = "ID_etab_class")

dim(joined)
```

- classes excluded classes excluded  classes < 5 and classes > 27

```{r}
# save

if(IMPUTED == "non-imputed"){
  if(NAOMIT == "True"){
save(joined, file = paste0("~/Data/cohort_",  ANNEE_COHORTE, "_", IMPUTED, "_joined_naomit_True.RData"))
  } else if (NAOMIT == "False"){
save(joined, file = paste0("~/Data/cohort_",  ANNEE_COHORTE, "_", IMPUTED, "_joined_naomit_False.RData"))
    }
}

if(IMPUTED == "imputed"){
save(joined, file = paste0("~/Data/cohort_", ANNEE_COHORTE, "_", IMPUTED, "_joined.RData"))
}
```

# SAVE joined_n

```{r}
# Joined_n : Decision with Benedict to take off children who are in advance or late, as they are very different from the others, while keeping variables with mean per class with their mean.

joined_n <- joined[joined$Age_CP >= AGE_PRECOCE & joined$Age_CP <= AGE_RETARD,]

# # Save Joined_n

if(IMPUTED == "non-imputed"){
  if(NAOMIT == "True"){
save(joined_n, file = paste0("~/Data/cohort_",  ANNEE_COHORTE, "_", IMPUTED, "_joined_n_naomit_True.RData"))
  } else if (NAOMIT == "False"){
save(joined_n, file = paste0("~/Data/cohort_",  ANNEE_COHORTE, "_", IMPUTED, "_joined_n_naomit_False.RData"))
    }
}

if(IMPUTED == "imputed"){
save(joined_n, file = paste0("~/Data/cohort_", ANNEE_COHORTE, "_", IMPUTED, "_joined_n.RData"))
}

dim(joined_n)

```

# SAVE Joined30 

= Select only classes with minimum of 30% of boys and 30% of girls 

```{r}

if(IMPUTED == "non-imputed"){
  if(NAOMIT == "True"){

joined30 <- joined[(joined$boy_proportion >= 0.30) & (joined$boy_proportion <= 0.70) , ]
save(joined30, file = paste0("~/Data/cohort_",  ANNEE_COHORTE, "_non-imputed_joined30_naomit_True.RData"))

  } else if (NAOMIT == "False"){

joined30 <- joined[(joined$boy_proportion >= 0.30) & (joined$boy_proportion <= 0.70) , ]
save(joined30, file = paste0("~/Data/cohort_", ANNEE_COHORTE,"_non-imputed_joined30_naomit_False.RData"))

  }
}

if(IMPUTED == "imputed"){

joined30 <- joined[(joined$boy_proportion >= 0.30) & (joined$boy_proportion <= 0.70) , ]
save(joined30, file = paste0("~/Data/cohort_",  ANNEE_COHORTE, "_imputed_joined30.RData"))

}

dim(joined30)

```

# SAVE Joined30_n

```{r}

if(IMPUTED == "non-imputed"){
  if(NAOMIT == "True"){

joined30_n <- joined_n [ (joined_n$boy_proportion >= 0.30) & (joined_n$boy_proportion <= 0.70) , ]
save(joined30_n, file = paste0("~/Data/cohort_",  ANNEE_COHORTE, "_non-imputed_joined30_n_naomit_True.RData"))

  } else if (NAOMIT == "False"){

joined30_n <- joined_n [ (joined_n$boy_proportion >= 0.30) & (joined_n$boy_proportion <= 0.70) , ]
save(joined30_n, file = paste0("~/Data/cohort_", ANNEE_COHORTE,"_non-imputed_joined30_n_naomit_False.RData"))

  }
}

if(IMPUTED == "imputed"){

joined30_n <- joined_n [ (joined_n$boy_proportion >= 0.30) & (joined_n$boy_proportion <= 0.70) , ]
save(joined30_n, file = paste0("~/Data/cohort_",  ANNEE_COHORTE, "_imputed_joined30_n.RData"))

}

dim(joined30_n)
```

