---
title: "8_Data_Models_reg"
author: Pauline Martinot [UNICOG, NeuroSpin]
date: "09/01/2022"
output:
  pdf_document:
    toc: yes
    toc_depth: 3
  html_document:
    toc: yes
    toc_depth: '3'
    df_print: paged
---


Note 11/10/2023 : I added 4 math tests at T1 in the Gaussianization process for the matching figures and experiments. Due to the happening of NANs I could not explained, I decided to impute the fewer NANs with Mice.
Therefore giving the new Gau_joined_Mice.RData

However, all models and figures have been undergoing Gaussianization process without the burden of the additional math assessments at T1, and therefore did not need any imputation process. 

### Parameters

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

# Parameters to set before launch of the pipeline

ANNEE_COHORTE = "2018" # 2019 # 2020
IMPUTED =  "imputed"# "non-imputed" 

# Library
library(ggplot2)
library(FactoMineR)
library(dplyr)
library(tidyverse)
library(broom)
library(jtools)
library(LambertW)
library(reshape2)

```

# Data = joined

Step 1 : Selecting children in classes containing 6 to 27 children per class and, selecting children of normal age when starting first grade = Removing classes with an extreme size (n < 5 or n > 28 children per class)  

Step 2 : As variables are made per class, computing the following class-level variables: boys’ proportion per class, gender of first of class

End of script // 3 //

Step 3 : Gaussianizing individual variables (a mean of 0 and a standard deviation of 1) 

Step 4 : Computing following class-level variables = heterogeneity both in math and in language at T1

Step 5 : Select age min 64 and age Max 86 // Fig 1 // 

Step 6 : Select children of normal age : Removing children outside the normal age range (< 69- or > 80 month-old)  // Fig 2 & 3 & Matching // 

Step 7 : if needed, removing classes with less than 30% of boys and 30% of girls // Fig 3 and model //


```{r}
load(file = paste0("~/Desktop/education/ ARTICLE_Final_script/data/cohort_", ANNEE_COHORTE,"_imputed_joined.RData"))

```


### + sanity check 

```{r echo=TRUE}

summary(joined$Taille_Classe)    # min 6 and max 27
summary(joined$n_girls)          # min 0 max 22-24
summary(joined$n_boy)            # min 0 max 22-24
summary(joined$boy_proportion)   # 0 to 1

```


### + Rename Sexe as Sexe_Boys for facilitating comprehension when reading results

```{r}

# Sexe_Num (-0.5 ; +0.5) vs. Sexe (Boys ;Girls) => Sexe_Boys (Boys, Girls)

names(joined)[names(joined) == "Sexe"] <- "Sexe_Boys" 
joined$Sexe_Boys <- as.factor(joined$Sexe_Boys)
summary(joined$Sexe_Boys)

# in 2018 we end up with Sexe_Num as numeric (-0.5 to 0.5) and Sexe_Boys as factor (Boys or Girls)
```

### + Add Age

We keep "Age_CP" in Gaussianized data for multilevel models

However, for the figures (3A and co) we keep 3 ages : Age at T1, Age at T2 and Age at T3, that are not gaussianized

```{r}

# sanity check

summary(joined$Age_CP) # (2018) 51-98

# Duplicate Age at T1 column   = Create duplicate of column with new name

joinedew <- joined %>%         
  mutate(Age_T1 = Age_CP)

rm(joined)
joined <- joinedew
rm(joinedew)

summary(joined$Age_CP) # (2018) 51-98
summary(joined$Age_T1) # (2018) 51-98

# Duplicate IPS   = Create duplicate of column with new name

joinedew <- joined %>%         
  mutate(IPS = IPS_Etab_CP)

rm(joined)
joined <- joinedew
rm(joinedew)

summary(joined$IPS_Etab_CP) # (2018) 51-98
summary(joined$IPS) # (2018) 51-98

# Add additional column for Age at T2 and Age at T3

# names(joined)[names(joined) == "Age_CP"] <- "Age_T1"

joined$IPS            <- as.numeric(joined$IPS)
joined$IPS_Etab_CP    <- as.numeric(joined$IPS_Etab_CP)
joined$Age_CP <- as.numeric(joined$Age_CP)
joined$Age_T1 <- as.numeric(joined$Age_T1)
joined$Age_T2 <- as.numeric(joined$Age_T1 + 4)
joined$Age_T3 <- as.numeric(joined$Age_T1 + 12)

summary(joined$Age_CP)
summary(joined$Age_T1)
summary(joined$Age_T2)
summary(joined$Age_T3)

```


### + Data pre selection

```{r echo=TRUE}

nrow(joined[is.na(joined$T1_Lire_Nombre_P), ]) # n = 0

Math_T1 <- c("T1_Ecri_Nombre_P",
             "T1_Lire_Nombre_P",
             "T1_Resoud_Pb_P",
             "T1_Denombrer_P",
             "T1_Compa_Nombre_P",
             "T1_Ligne_Num_P")

joined <- joined[ , c("ID_Eleve","ID_etab_class", "T1_Math", "T2_Math", "T3_Math", Math_T1,
                      "T2_Ligne_Num_P", "T3_Ligne_Num_P", "T2_Resoud_Pb_P", "T3_Resoud_Pb_P",
                              "T1_Language", "T2_Language", "T3_Language",
                              "IPS_Etab_CP", "IPS", "Sexe_Boys", "Sexe_Num",
                              "Age_CP", "Age_T1", "Age_T2", "Age_T3",
                              "boy_proportion","Taille_Classe",
                              "First_sexe_in_T1_Math", "First_sexe_in_T1_Language",
                              "First_mean_sexe_in_T1_Math", "First_mean_sexe_in_T1_Language",
                               "Categ_Etab_CP" , "Categ_10c_CP", "first_in_T1_Math")]

joined$Taille_Classe <- as.numeric(joined$Taille_Classe)


```

### + 1) Gaussianize Variables 

To gaussianize :

- "T1_Math", "T2_Math", "T3_Math", + math_T1
- "T1_Ligne_Num", "T2_Ligne_Num", "T3_Ligne_Num",
- "T1_Resoud_Pb", "T2_Resoud_Pb", "T3_Resoud_Pb",
- "T1_Language", "T2_Language", "T3_Language",
- IPS_Etab_CP
- Age_CP
- boy_proportion
- Taille_Classe
- First_sexe_in_T1_Math
- First_sexe_in_T1_Language

Keep off the others : "ID_etab_class", "Sexe_Boys", "Sexe_Num", "ID_Eleve", "Categ_Etab_CP" , "Categ_10c_CP"
- Age_T1, Age_T2, Age_T3

```{r echo=TRUE}

                            
joined_gau    <- as.data.frame(Gaussianize(joined[, c("T1_Math", "T2_Math", "T3_Math", "T1_Ecri_Nombre_P", "T1_Resoud_Pb_P",
                                                    "T1_Denombrer_P", "T1_Compa_Nombre_P", "T1_Ligne_Num_P", "T2_Ligne_Num_P",
                                                    "T3_Ligne_Num_P", "T2_Resoud_Pb_P", "T3_Resoud_Pb_P", "T1_Language",
                                                    "T2_Language", "T3_Language", "Age_CP", "IPS_Etab_CP", "boy_proportion",
                                                    "Taille_Classe")],
                                         type = c("s"), method = c("IGMM"), return.u = TRUE))


```


```{r echo=TRUE}


names(joined_gau)[names(joined_gau) == "T1_Math.U"]                       <- "T1_Math"
names(joined_gau)[names(joined_gau) == "T2_Math.U"]                       <- "T2_Math"
names(joined_gau)[names(joined_gau) == "T3_Math.U"]                       <- "T3_Math"

names(joined_gau)[names(joined_gau) == "T1_Ligne_Num_P.U"]                <- "T1_Ligne_Num_P"
names(joined_gau)[names(joined_gau) == "T2_Ligne_Num_P.U"]                <- "T2_Ligne_Num_P"
names(joined_gau)[names(joined_gau) == "T3_Ligne_Num_P.U"]                <- "T3_Ligne_Num_P"

names(joined_gau)[names(joined_gau) == "T1_Resoud_Pb_P.U"]                <- "T1_Resoud_Pb_P"
names(joined_gau)[names(joined_gau) == "T2_Resoud_Pb_P.U"]                <- "T2_Resoud_Pb_P"
names(joined_gau)[names(joined_gau) == "T3_Resoud_Pb_P.U"]                <- "T3_Resoud_Pb_P"

names(joined_gau)[names(joined_gau) == "T1_Language.U"]                   <- "T1_Language"
names(joined_gau)[names(joined_gau) == "T2_Language.U"]                   <- "T2_Language"
names(joined_gau)[names(joined_gau) == "T3_Language.U"]                   <- "T3_Language"

names(joined_gau)[names(joined_gau) == "T1_Ecri_Nombre_P.U"]              <- "T1_Ecri_Nombre_P"
# names(joined_gau)[names(joined_gau) == "T1_Lire_Nombre_P.U"]              <- "T1_Lire_Nombre_P"
names(joined_gau)[names(joined_gau) == "T1_Denombrer_P.U"]                <- "T1_Denombrer_P"
names(joined_gau)[names(joined_gau) == "T1_Compa_Nombre_P.U"]             <- "T1_Compa_Nombre_P"

names(joined_gau)[names(joined_gau) == "IPS_Etab_CP.U"]                   <- "IPS_Etab_CP"
names(joined_gau)[names(joined_gau) == "Age_CP.U"]                        <- "Age_CP"
names(joined_gau)[names(joined_gau) == "boy_proportion.U"]                <- "boy_proportion"
names(joined_gau)[names(joined_gau) == "Taille_Classe.U"]                 <- "Taille_Classe"
#names(joined_gau)[names(joined_gau) == "First_sexe_in_T1_Math.U"]         <- "First_sexe_in_T1_Math"
#names(joined_gau)[names(joined_gau) == "First_sexe_in_T1_Language.U"]     <- "First_sexe_in_T1_Language"

joined_gau$T1_Math                       <- as.numeric(joined_gau$T1_Math)
joined_gau$T2_Math                       <- as.numeric(joined_gau$T2_Math)
joined_gau$T3_Math                       <- as.numeric(joined_gau$T3_Math)
joined_gau$T1_Ligne_Num_P                <- as.numeric(joined_gau$T1_Ligne_Num_P)
joined_gau$T2_Ligne_Num_P                <- as.numeric(joined_gau$T2_Ligne_Num_P)
joined_gau$T3_Ligne_Num_P                <- as.numeric(joined_gau$T3_Ligne_Num_P)
joined_gau$T1_Resoud_Pb_P                <- as.numeric(joined_gau$T1_Resoud_Pb_P)
joined_gau$T2_Resoud_Pb_P                <- as.numeric(joined_gau$T2_Resoud_Pb_P)
joined_gau$T3_Resoud_Pb_P                <- as.numeric(joined_gau$T3_Resoud_Pb_P)
joined_gau$T1_Ecri_Nombre_P              <- as.numeric(joined_gau$T1_Ecri_Nombre_P)
# joined_gau$T1_Lire_Nombre_P              <- as.numeric(joined_gau$T1_Lire_Nombre_P)
joined_gau$T1_Denombrer_P                <- as.numeric(joined_gau$T1_Denombrer_P)
joined_gau$T1_Compa_Nombre_P             <- as.numeric(joined_gau$T1_Compa_Nombre_P)

joined_gau$T1_Language                 <- as.numeric(joined_gau$T1_Language)
joined_gau$T2_Language                 <- as.numeric(joined_gau$T2_Language)
joined_gau$T3_Language                 <- as.numeric(joined_gau$T3_Language)
joined_gau$IPS_Etab_CP                 <- as.numeric(joined_gau$IPS_Etab_CP)
joined_gau$Age_CP                      <- as.numeric(joined_gau$Age_CP)
joined_gau$boy_proportion              <- as.numeric(joined_gau$boy_proportion)
joined_gau$Taille_Classe               <- as.numeric(joined_gau$Taille_Classe)

#joined_gau$First_sexe_in_T1_Math       <- as.numeric(joined_gau$First_sexe_in_T1_Math)
#joined_gau$First_sexe_in_T1_Language   <- as.numeric(joined_gau$First_sexe_in_T1_Language)

```

### + 2) Add Gaussianize and non Gaussianized

"ID_etab_class", "Sexe_Boys", "Sexe_Num", "ID_Eleve", "Categ_Etab_CP" , "Categ_10c_CP", "Age_T1", "Age_T2", "Age_T3"
"First_sexe_in_T1_Math", "First_sexe_in_T1_Language"
+ "boy_prop", "Age_CAT"

```{r echo=TRUE}

# Creating Boy_Prop

joinedew <- joined %>%         
  mutate(boy_prop = boy_proportion)
rm(joined)
joined <- joinedew
rm(joinedew)
joined$boy_prop <- as.numeric(joined$boy_prop)

# Creating Age_CAT

summary(joined$Age_CP)
joined$Age_CAT <- case_when((joined$Age_CP < 69) ~ "Young",
                              (joined$Age_CP > 68 & joined$Age_CP < 81) ~ "Normal",
                              (joined$Age_CP > 80) ~ "Late")

joined$Age_CAT   <- as.factor(joined$Age_CAT)
summary(joined$Age_CAT)

# Gathering gaussianized and non gaussianized variables

Base <- joined[, c("ID_etab_class", "Sexe_Boys", "Sexe_Num", "ID_Eleve", "Categ_Etab_CP","Categ_10c_CP", "Age_T1", "Age_T2", "Age_T3", "boy_prop", "Age_CAT" , "IPS_Etab_CP", "first_in_T1_Math", "First_sexe_in_T1_Math", "First_sexe_in_T1_Language", "First_mean_sexe_in_T1_Math", "First_mean_sexe_in_T1_Language")]

names(joined_gau)[names(joined_gau) == "IPS_Etab_CP"]                 <- "IPS"

joined_base_gaussian_3 <- cbind(Base, joined_gau)
rm(Base, joined_gau)
glimpse(joined_base_gaussian_3)

# Missmatch to correct for Sexe / Sexe_Boys

joined_base_gaussian_3$Sexe_Num      <- as.numeric(joined_base_gaussian_3$Sexe_Num)
joined_base_gaussian_3$Sexe_Boys     <- as.factor(joined_base_gaussian_3$Sexe_Boys)
joined_base_gaussian_3$Categ_Etab_CP <- as.factor(joined_base_gaussian_3$Categ_Etab_CP)
joined_base_gaussian_3$Categ_10c_CP  <- as.factor(joined_base_gaussian_3$Categ_10c_CP)
joined_base_gaussian_3$boy_prop      <- as.numeric(joined_base_gaussian_3$boy_prop)
joined_base_gaussian_3$Age_CAT       <- as.factor(joined_base_gaussian_3$Age_CAT)
joined_base_gaussian_3$Age_CP        <- as.numeric(joined_base_gaussian_3$Age_CP)
joined_base_gaussian_3$Age_T1        <- as.numeric(joined_base_gaussian_3$Age_T1)
joined_base_gaussian_3$IPS           <- as.numeric(joined_base_gaussian_3$IPS)

joined_base_gaussian_3$first_in_T1_Math  <- as.factor(joined_base_gaussian_3$first_in_T1_Math)

joined_base_gaussian_3$First_sexe_in_T1_Math       <- as.numeric(joined_base_gaussian_3$First_sexe_in_T1_Math)
joined_base_gaussian_3$First_sexe_in_T1_Language   <- as.numeric(joined_base_gaussian_3$First_sexe_in_T1_Language)
joined_base_gaussian_3$First_mean_sexe_in_T1_Math       <- as.numeric(joined_base_gaussian_3$First_mean_sexe_in_T1_Math)
joined_base_gaussian_3$First_mean_sexe_in_T1_Language   <- as.numeric(joined_base_gaussian_3$First_mean_sexe_in_T1_Language)

```

### + 3) Heterogeneity

After T1_Math is gaussianized  => create Heterogeneity_T1_Math and Heterogeneity_T1_Language

```{r echo=TRUE}


# 1) compute sd for Math at T1 = Heterogeneity in Math at T1

reversed_table <- melt(joined_base_gaussian_3[, c("T1_Math","ID_etab_class")], id = c("ID_etab_class"))
heterogeneities <- dcast(reversed_table, ID_etab_class ~ variable, sd)
names(heterogeneities) <- c("ID_etab_class", paste0("heterogeneity_",  c("T1_Math")))

# merge heterogeneities and main classes table
joined_base_gau_hetero_3 <- merge(joined_base_gaussian_3, heterogeneities[ , c("ID_etab_class", "heterogeneity_T1_Math")],
                 by = "ID_etab_class")

mean(joined_base_gau_hetero_3$heterogeneity_T1_Math) #0.86
sd(joined_base_gau_hetero_3$heterogeneity_T1_Math) #0.20

joined_hetero_Math_3  <- as.data.frame(Gaussianize(joined_base_gau_hetero_3[, c("heterogeneity_T1_Math")],
                                         type = c("s"), method = c("IGMM"), return.u = TRUE))

mean(joined_hetero_Math_3$Y1.U) #0
sd(joined_hetero_Math_3$Y1.U) #1

names(joined_hetero_Math_3)[names(joined_hetero_Math_3) == "Y1.U"] <- "heterogeneity_T1_Math_New"

Base <- joined[, c("ID_etab_class")]

rm(heterogeneities, reversed_table)

joined_base_gau_H_3 <- cbind(joined_base_gaussian_3, joined_hetero_Math_3)
names(joined_base_gau_H_3)[names(joined_base_gau_H_3) == "heterogeneity_T1_Math_New"] <- "heterogeneity_T1_Math"

# 1) compute sd for Language at T1 = Heterogeneity in Language at T1

reversed_table <- melt(joined_base_gaussian_3[, c("T1_Language","ID_etab_class")], id = c("ID_etab_class"))
heterogeneities <- dcast(reversed_table, ID_etab_class ~ variable, sd)
names(heterogeneities) <- c("ID_etab_class", paste0("heterogeneity_",  c("T1_Language")))

# merge heterogeneities and main classes table
joined_base_gau_hetero_lang_3 <- merge(joined_base_gaussian_3, heterogeneities[ , c("ID_etab_class", "heterogeneity_T1_Language")],
                 by = "ID_etab_class")

mean(joined_base_gau_hetero_lang_3$heterogeneity_T1_Language) #0.84
sd(joined_base_gau_hetero_lang_3$heterogeneity_T1_Language) #0.18

joined_hetero_Lang_3  <- as.data.frame(Gaussianize(joined_base_gau_hetero_lang_3[, c("heterogeneity_T1_Language")],
                                         type = c("s"), method = c("IGMM"), return.u = TRUE))

mean(joined_hetero_Lang_3$Y1.U) #0
sd(joined_hetero_Lang_3$Y1.U) #1

names(joined_hetero_Lang_3)[names(joined_hetero_Lang_3) == "Y1.U"] <- "heterogeneity_T1_Lang_New"


rm(heterogeneities, reversed_table)

joined_base_gau_Fin_3 <- cbind(joined_base_gau_H_3, joined_hetero_Lang_3)
names(joined_base_gau_Fin_3)[names(joined_base_gau_Fin_3) == "heterogeneity_T1_Lang_New"] <- "heterogeneity_T1_Lang"

rm(joined_base_gaussian_3, joined_base_gau_H_3, joined_base_gau_hetero_3, joined_base_gau_hetero_lang_3, joined_hetero_Lang_3, joined_hetero_Math_3)

Joined_Fin_3 <- joined_base_gau_Fin_3

rm(joined_base_gau_Fin_3)

glimpse(Joined_Fin_3)

```



### + 4) Detailed DATA

classes ( > 5 to < 28 per class) 

joined : data from "joined" in the SCRIPT #3 all ages from 51 to 99 months

Joined_Fin_3 : data Gaussianized from joined 

DATA_AGE_gau_Base_n : data Gau from joined then selection on Normal age (69 to 80 months both included)
Decision with Benedict to take off children who are in advance or late, as they are very different from the others, while keeping variables with mean per class with their mean.

DATA_AGE_gau_Base_30n : data Gau from joined then selection on normal age, then Selected classes with min 30% of boys and 30% of girls 

```{r}

summary(Joined_Fin_3$Age_T1) # 51-98

# select Normal age at T1

DATA_AGE_gau_Base_n = Joined_Fin_3[(Joined_Fin_3$Age_T1 >= 69) & (Joined_Fin_3$Age_T1 <= 80) ,]
summary(DATA_AGE_gau_Base_n$Age_T1)
glimpse(DATA_AGE_gau_Base_n)

# select Normal age at T1 + classes 30% boys/girls

summary(DATA_AGE_gau_Base_n$boy_prop)
typeof(DATA_AGE_gau_Base_n$boy_prop)
DATA_AGE_gau_Base_30n = DATA_AGE_gau_Base_n[(DATA_AGE_gau_Base_n$boy_prop >= 0.30000) & (DATA_AGE_gau_Base_n$boy_prop <= 0.70000) ,]
summary(DATA_AGE_gau_Base_30n$boy_prop)


```

### + 5) Save DATA 

classes ( > 5 to < 28 per class) 

joined : data from "joined" in the SCRIPT #3 all ages from 51 to 99 months

Joined_Fin_3 : data Gaussianized from joined 

DATA_AGE_gau_Base_n : data Gau from joined then selection on Normal age (69 to 80 months both included)
Decision with Benedict to take off children who are in advance or late, as they are very different from the others, while keeping variables with mean per class with their mean.

DATA_AGE_gau_Base_30n : data Gau from joined then selection on normal age, then Selected classes with min 30% of boys and 30% of girls 

```{r}

save.image(file = paste0("~/Data/cohort_", ANNEE_COHORTE, "_", IMPUTED, "_ModRegLin_Gau_From_joined_VF.RData"))

```

