---
title: "2bis. Total 2_3_4 for 2019_2020"
author:
  - Pauline Martinot [UNICOG, NeuroSpin]
date: "July 2023"
output:
  pdf_document:
    toc: yes
  html_document:
    number_sections: no
    toc: yes
    toc_depth: 2
abstract: | 
  This notebook concerns data from National assessment in 1st and 2nd grade in France : Composite covariate creation. This notebook comes after the preprocessing notebook, and create all the composite covariates, along with normalization of grades, and creation of the rank covariates. The input can be either an imputed data set, or a data set filtered from the missing values as detailed in preprocess.
---


## Load DATA 

Selected classes are 
- from 6 to 27 children per class
- with normal Age in first grade (69 to 80 mo included)
- minimum with 30% of boys or 30% of girls = to be tested 



Data from SCRIPT 3
- joined
- FROM : imputed_after_2_composite_covariate.RData
- Math : mean in percentage 0 to 100

Data from joined with Gaussianization
- Joined_Fin_3
- GAUSSIANIZED : Gaussianize function applied to all numerical variables

Data from Joined_Fin_3 with selection on Normal age 
- DATA_AGE_gau_Base_n

Data from Joined_Fin_3 with _n and selection on 30% boys/girls
- DATA_AGE_gau_Base_n_30n 


```{r}
knitr::opts_chunk$set(echo = TRUE)

# Parameters to set before launch of the pipeline

ANNEE_COHORTE = "2018" # 2019 #2020

library(tidyverse)
library(dplyr)
library(reshape2)
library(MatchIt)
library(patchwork)
library(lmerTest)
library(glmertree)
library(performance)
library(broom)



# load(file = paste0("~/Data/cohort_", ANNEE_COHORTE, "_imputed_ModRegLin_Article.RData"))

load("~/Data/cohort_2018_imputed_ModRegLin_Gau_From_joined.RData")



```

```{r}

glimpse(DATA_AGE_gau_Base_n)

```

ici essai avec population age normal = DATA_AGE_gau_Base_n


# 1) T3 Math empty and progressive models


```{r echo=TRUE}
model1 <- lmer(T3_Math ~ 1 + (1 | ID_etab_class),
                 data = DATA_AGE_gau_Base_n,  REML = FALSE)
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/MultiLevel_Model_", ANNEE_COHORTE, "_T3_Math_Empty_Class.csv"), row.names = F)

model2 <- lmer(T3_Math ~ 1 + (1 + T1_Math | ID_etab_class),
                 data = DATA_AGE_gau_Base_n,  REML = FALSE)
summary(model2)
m2 <- coef(summary(model2))
m2
write.csv2(m2, file= paste0("~/table/MultiLevel_Model_", ANNEE_COHORTE, "_T3_Math_Simple_m4.csv"), row.names = F)

model3 <- lmer(T3_Math ~ 1 + (1 + Sexe_Num | ID_etab_class), 
                 data = DATA_AGE_gau_Base_n,  REML = FALSE)
summary(model3)
m3 <- coef(summary(model3))
m3
write.csv2(m3, file= paste0("~/table/MultiLevel_Model_", ANNEE_COHORTE, "_T3_Math_Empty_GenderSexe_Num.csv"), row.names = F)

model4 <- lmer(T3_Math ~ T1_Math + (1 + T1_Math | ID_etab_class), 
                 data = DATA_AGE_gau_Base_n,  REML = FALSE)
summary(model4)
m4 <- coef(summary(model4))
m4
write.csv2(m4, file= paste0("~/table/MultiLevel_Model_", ANNEE_COHORTE, "_T3_Math_Empty_Math.csv"), row.names = F)

model5 <- lmer(T3_Math ~ Sexe_Num + (1 + Sexe_Num | ID_etab_class), 
                 data = DATA_AGE_gau_Base_n,  REML = FALSE)
summary(model5)
m5 <- coef(summary(model5))
m5
write.csv2(m4, file= paste0("~/table/MultiLevel_Model_", ANNEE_COHORTE, "_T3_Math_Empty_Math.csv"), row.names = F)

model6 <- lmer(T3_Math ~ 1 + (1 + T1_Math + Sexe_Num | ID_etab_class), 
                 data = DATA_AGE_gau_Base_n,  REML = FALSE)

summary(model6)
m6 <- coef(summary(model6))
write.csv2(m6, file= paste0("~/table/MultiLevel_Model_", ANNEE_COHORTE, "_T3_Math_n_Mod1.csv"), row.names = F)

rm(model1, model2, model3, model4, model5, model6)
rm(m1, m2, m3, m4, m5, m6)

# empty interactions

model1 <- lmer(T3_Math ~ T1_Math*Sexe_Num +
                 (1 | ID_etab_class), 
                 data = DATA_AGE_gau_Base_n,  REML = FALSE)
summary(model1)
m1 <- coef(summary(model1))
m1

# empty interaction + T1Math random

model2 <- lmer(T3_Math ~
                 Sexe_Num*T1_Math +
                 (1 + T1_Math | ID_etab_class), 
                 data = DATA_AGE_gau_Base_n,  REML = FALSE)
summary(model2)
m2 <- coef(summary(model2))
m2

# empty interaction + Sexe_Num random

model3 <- lmer(T3_Math ~
                 Sexe_Num*T1_Math +
                 (1 + Sexe_Num | ID_etab_class), 
                 data = DATA_AGE_gau_Base_n,  REML = FALSE)
summary(model3)
m3 <- coef(summary(model3))
m3

# empty interaction + T1 math and Sexe_Num random

model4 <- lmer(T3_Math ~
                 Sexe_Num*T1_Math +
                 (1 + T1_Math + Sexe_Num | ID_etab_class), 
                 data = DATA_AGE_gau_Base_n,  REML = FALSE)
summary(model4)
m4 <- coef(summary(model4))
m4

### B. T3 Math = var indiv

model2 <- lmer(T3_Math ~ 
                 Age_CP +
                 Sexe_Num +
                 T1_Math +
                 # T1_Language +
                 (1 + T1_Math + Sexe_Num | ID_etab_class), 
                 data = DATA_AGE_gau_Base_n,  REML = FALSE)

summary(model2)
m2 <- coef(summary(model2))
write.csv2(m2, file= paste0("~/table/MultiLevel_Model_", ANNEE_COHORTE, "_T3_Math_n_Mod2.csv"), row.names = F)

rm( m2)


### C. T3 Math = var indiv + var collec

model2 <- lmer(T3_Math ~ 
                 Age_CP +
                 Sexe_Num +
                 T1_Math +
                 # T1_Language +

                 First_sexe_in_T1_Math +
                 IPS_Etab_CP +
                 Taille_Classe +
                 boy_proportion +
                 heterogeneity_T1_Math +
                 
                 (1 + T1_Math + Sexe_Num | ID_etab_class), 
                 data = DATA_AGE_gau_Base_n,  REML = FALSE)

summary(model2)
m2 <- coef(summary(model2))
write.csv2(m2, file= paste0("~/table/MultiLevel_Model_", ANNEE_COHORTE, "_T3_Math_n_Mod3.csv"), row.names = F)

rm( m2)

model2 <- lmer(T3_Math ~ 
                 T1_Math +
                 Sexe_Num +
                 T1_Language +
                 Age_CP +
                 IPS_Etab_CP +
                 First_sexe_in_T1_Math +
                 boy_proportion +
                 Taille_Classe +
                 heterogeneity_T1_Math +
                 
                 Sexe_Num*Age_CP +
                 Sexe_Num*T1_Math +
                 Sexe_Num*T1_Language +
                 Sexe_Num*heterogeneity_T1_Math +
                 Sexe_Num*Taille_Classe +
                 Sexe_Num*boy_proportion +
                 Sexe_Num*First_sexe_in_T1_Math +
                 Sexe_Num*IPS_Etab_CP +
                 
                 
                 (1 + T1_Math + Sexe_Num | ID_etab_class), 
                 data = DATA_AGE_gau_Base_n,  REML = FALSE)

summary(model2)
m2 <- coef(summary(model2))
write.csv2(m2, file= paste0("~/table/MultiLevel_Model_", ANNEE_COHORTE, "_T3_Math_n_Mod4.csv"), row.names = F)

rm( m2)

```



# Math models 



# 1) T1 Math


```{r}

model1 <- lmer(T1_Math ~

                 Age_CP +
                 Sexe_Num +
                 # T1_Language +
                 IPS_Etab_CP +
                 Taille_Classe +
                 boy_proportion +
                 # First_sexe_in_T1_Math +
                 
                 Sexe_Num*Age_CP +
                 # Sexe_Num*T1_Language +
                 # Sexe_Num*First_sexe_in_T1_Math +
                 Sexe_Num*IPS_Etab_CP +
                 Sexe_Num*Taille_Classe +
                 Sexe_Num*boy_proportion +
                   
                 (1 + Sexe_Num  | ID_etab_class),
               data = DATA_AGE_gau_Base_n,  REML = FALSE)
               
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/MultiLevel_Model_", ANNEE_COHORTE, "_T1_Math_final.csv"), row.names = F)
rm(model1, m1)

```




# 2) T2 Math


```{r}

model1 <- lmer(T2_Math ~

                 T1_Language +
                 T1_Math +
                 Sexe_Num +
                 Age_CP+ # Age_CP does not work 
                 
                 First_sexe_in_T1_Math +
                 boy_proportion +
                 Taille_Classe +
                 IPS_Etab_CP +
                 heterogeneity_T1_Math +
                 
                 Sexe_Num*T1_Language +
                 Sexe_Num*T1_Math +
                 Sexe_Num*Age_CP +
                 Sexe_Num*First_sexe_in_T1_Math +
                 Sexe_Num*boy_proportion+
                 Sexe_Num*Taille_Classe +
                 Sexe_Num*IPS_Etab_CP +
                 Sexe_Num*heterogeneity_T1_Math +
                 
                   
                 (1 + T1_Math + Sexe_Num  | ID_etab_class), 
                 data = DATA_AGE_gau_Base_n,  REML = FALSE)

summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/MultiLevel_Model_", ANNEE_COHORTE, "_T2_Math_Final.csv"), row.names = F)
rm(model1, m1)

```


# 3) T3 Math Gender gap _ Final model

Age_CP does not work so I replace it with Age_T1 that we transformed into a numerical variable. there will be the need to transform it again in factor for the figures
 
```{r}

DATA_AGE_gau_Base_n$Age_CP <- as.numeric(DATA_AGE_gau_Base_n$Age_CP)
DATA_AGE_gau_Base_n$Sexe_Boys <- factor(DATA_AGE_gau_Base_n$Sexe_Boys, levels = c('Boys', 'Girls'))
levels(DATA_AGE_gau_Base_n$Sexe_Boys)

model1 <- lmer(T3_Math ~

                 T1_Language +
                 T1_Math +
                 Sexe_Num +
                 IPS_Etab_CP +
                 Age_CP + # Age_CP does not work 
                 heterogeneity_T1_Math +
                 boy_proportion +
                 First_sexe_in_T1_Math +
                 Taille_Classe +
                 
                 Sexe_Num*T1_Language +
                 Sexe_Num*T1_Math +
                 Sexe_Num*IPS_Etab_CP +
                 Sexe_Num*Age_CP +
                 Sexe_Num*heterogeneity_T1_Math +
                 Sexe_Num*boy_proportion+
                 Sexe_Num*First_sexe_in_T1_Math +
                 Sexe_Num*Taille_Classe +

                 (1 + T1_Math + Sexe_Num  | ID_etab_class), 
                 data = DATA_AGE_gau_Base_n,  REML = FALSE)

summary(model1)
m1 <- coef(summary(model1))

write.csv2(m1, file= paste0("~/table/MultiLevel_Model_", ANNEE_COHORTE, "_T3_Math_Model8_Final_avec_langageT1.csv"), row.names = F)

hist(DATA_AGE_gau_Base_n$Age_CP)

```






# Language models



# 1) T1 Lang


```{r}

model1 <- lmer(T1_Language ~

                 Age_CP +
                 Sexe_Num +

                 First_sexe_in_T1_Language +
                 IPS_Etab_CP +
                 Taille_Classe +
                 boy_proportion +
                 
                 Sexe_Num*Age_CP +
                 Sexe_Num*First_sexe_in_T1_Language +
                 Sexe_Num*IPS_Etab_CP +
                 Sexe_Num*Taille_Classe +
                 Sexe_Num*boy_proportion +
                   
                 (1 + Sexe_Num  | ID_etab_class),
               data = DATA_AGE_gau_Base_n,  REML = FALSE)
               
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/MultiLevel_Model_", ANNEE_COHORTE, "_T1_LANG_Final.csv"), row.names = F)
rm(model1, m1)

```




# 2) T2 Lang


```{r}

model1 <- lmer(T2_Language ~

                 Age_CP +
                 Sexe_Num +
                 T1_Math +
                 T1_Language +

                 First_sexe_in_T1_Language +
                 IPS_Etab_CP +
                 Taille_Classe +
                 boy_proportion +
                 heterogeneity_T1_Lang +

                 Sexe_Num*Age_CP +
                 Sexe_Num*T1_Math +
                 Sexe_Num*T1_Language +
                 Sexe_Num*First_sexe_in_T1_Language +
                 Sexe_Num*IPS_Etab_CP +
                 Sexe_Num*Taille_Classe +
                 Sexe_Num*boy_proportion+
                 Sexe_Num*heterogeneity_T1_Lang +
                 

                   
                 (1 + T1_Language + Sexe_Num  | ID_etab_class), 
                 data = DATA_AGE_gau_Base_n,  REML = FALSE)

summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/MultiLevel_Model_", ANNEE_COHORTE, "_T2_LANG_Final.csv"), row.names = F)
rm(model1, m1)

```


# 3) T3 Lang Gender gap _ Final model


```{r}

model1 <- lmer(T3_Language ~

                 Age_CP +
                 Sexe_Num +
                 T1_Math +
                 T1_Language +

                 First_sexe_in_T1_Language +
                 IPS_Etab_CP +
                 Taille_Classe +
                 boy_proportion +
                 heterogeneity_T1_Lang +
                 
                 Sexe_Num*Age_CP +
                 Sexe_Num*T1_Math +
                 Sexe_Num*T1_Language +
                 Sexe_Num*First_sexe_in_T1_Language +
                 Sexe_Num*IPS_Etab_CP +
                 Sexe_Num*Taille_Classe +
                 Sexe_Num*boy_proportion+
                 Sexe_Num*heterogeneity_T1_Lang +

                 (1 + T1_Language + Sexe_Num  | ID_etab_class), 
                 data = DATA_AGE_gau_Base_n,  REML = FALSE)

summary(model1)
m1 <- coef(summary(model1))

write.csv2(m1, file= paste0("~/table/MultiLevel_Model_", ANNEE_COHORTE, "_T3_LANG_Model9_Final.csv"), row.names = F)



```

