---
title: "Alpha Cronbach"
author: "Pauline MARTINOT"
date: "Juin 2023"
output: html_document
---


# Alpha Omega

Cronbach's alpha and McDonald's omega are widely used reliability or internal consistency measures in social, behavioral and education sciences. 

Alpha is reported in nearly every study that involves measuring a construct through multiple test items. 

The package 'coefficientalpha' calculates coefficient alpha and coefficient omega with missing data and non normal data. Robust standard errors and confidence intervals are also provided. A test is also available to test the tau-equivalent and homogeneous assumptions.


Cronbach's alpha and McDonald's omega are widely used reliability or internal consistency measures in social, behavioral and education sciences. 

Alpha is reported in nearly every study that involves measuring a construct through multiple test items. 

The package 'coefficientalpha' calculates coefficient alpha and coefficient omega with missing data and non normal data. Robust standard errors and confidence intervals are also provided. A test is also available to test the tau-equivalent and homogeneous assumptions.

```{r}
knitr::opts_chunk$set(echo = TRUE)

# Parameters to set before launch of the pipeline
# 
# ANNEE_COHORTE = "2021" # 2019 # 2020

knitr::opts_chunk$set(echo = TRUE, include = TRUE)

library(tidyverse)
library(dplyr)
library(ggplot2)
library(reshape2)
library(corrplot)
# install.packages("coefficientalpha")
# library(coefficientalpha)
library(psych)

load("~/Data/cohort_2018_imputed_joined_n.RData")

DATA_2018 <- joined_n[, c("ID_Eleve", "T1_Ecri_Nombre", "T1_Lire_Nombre", "T1_Resoud_Pb",
                          "T1_Denombrer", "T1_Compa_Nombre","T1_Ligne_Num", "T2_Compa_Nombre",
                          "T2_Ligne_Num", "T2_Addition", "T2_Soustract", "T2_Ecri_Nombre", "T2_Resoud_Pb",
                          "T3_Assemblage", "T3_Ligne_Num", "T3_Addition","T3_Soustract", "T3_Calcul_Mental", "T3_Ecri_Nombre")]
rm(joined_n)

load("~/Data/cohort_2019_imputed_joined_n.RData")

DATA_2019 <- joined_n[, c("ID_Eleve", "T1_Ecri_Nombre", "T1_Lire_Nombre", "T1_Resoud_Pb",
                          "T1_Denombrer", "T1_Compa_Nombre","T1_Ligne_Num", "T2_Compa_Nombre",
                          "T2_Ligne_Num", "T2_Addition", "T2_Soustract", "T2_Ecri_Nombre", "T2_Resoud_Pb",
                          "T3_Assemblage", "T3_Ligne_Num", "T3_Addition","T3_Soustract", "T3_Calcul_Mental", "T3_Ecri_Nombre")]
rm(joined_n)

load("~/Data/cohort_2020_imputed_joined_n.RData")
DATA_2020 <- joined_n[, c("ID_Eleve", "T1_Ecri_Nombre", "T1_Lire_Nombre", "T1_Resoud_Pb",
                          "T1_Denombrer", "T1_Compa_Nombre","T1_Ligne_Num", "T2_Compa_Nombre",
                          "T2_Ligne_Num", "T2_Addition", "T2_Soustract", "T2_Ecri_Nombre", "T2_Resoud_Pb",
                          "T3_Assemblage", "T3_Ligne_Num", "T3_Addition","T3_Soustract", "T3_Calcul_Mental", "T3_Ecri_Nombre")]
rm(classes, DATA_AGE_gau_Base_30n, DATA_AGE_gau_Base_n, data_depp, joined, Joined_Fin_3, joined30, joined30_n, joined_n,  m1, model1)

load("~/Data/cohort_2021_imputed_joined_n.RData")
DATA_2021 <- joined_n[, c("ID_Eleve", "T1_Ecri_Nombre", "T1_Lire_Nombre", "T1_Resoud_Pb",
                          "T1_Denombrer", "T1_Compa_Nombre","T1_Ligne_Num", "T2_Compa_Nombre",
                          "T2_Ligne_Num", "T2_Addition", "T2_Soustract", "T2_Ecri_Nombre", "T2_Resoud_Pb",
                          "T3_Assemblage", "T3_Ligne_Num", "T3_Addition","T3_Soustract", "T3_Calcul_Mental", "T3_Ecri_Nombre")]
rm(classes, DATA_AGE_gau_Base_30n, DATA_AGE_gau_Base_n, data_depp, joined, Joined_Fin_3, joined30, joined30_n, joined_n)




```



Cronbach's alpha and McDonald's omega are widely used reliability or internal consistency measures in social, behavioral and education sciences. 

Alpha is reported in nearly every study that involves measuring a construct through multiple test items. 

The package 'coefficientalpha' calculates coefficient alpha and coefficient omega with missing data and non normal data. Robust standard errors and confidence intervals are also provided. A test is also available to test the tau-equivalent and homogeneous assumptions.

### Data

```{r}

Math_T1 <- c("T1_Ecri_Nombre", "T1_Lire_Nombre", "T1_Resoud_Pb","T1_Denombrer", "T1_Compa_Nombre","T1_Ligne_Num")

Math_T2 <- c("T2_Compa_Nombre", "T2_Ligne_Num", "T2_Addition", "T2_Soustract", "T2_Ecri_Nombre", "T2_Resoud_Pb")

Math_T3 <- c("T3_Assemblage", "T3_Ligne_Num", "T3_Addition","T3_Soustract", "T3_Calcul_Mental", "T3_Ecri_Nombre")

```



### Alpha : Pop restreinte

```{r}

# Math T1

DATA_essai_T1       <- DATA_2018[ , c(Math_T1)]
DATA_restreinte_T1  <- sample_n(DATA_essai_T1, 50000) # sélectionner les 100 k 
resA_T1_2018        <- alpha(DATA_restreinte_T1, varphi = 0.1, se = FALSE) 

# Math T2

DATA_essai_T2       <- DATA_2018[ , c(Math_T2)]
DATA_restreinte_T2  <- sample_n(DATA_essai_T2, 50000) # sélectionner les 100 k 
resA_T2_2018        <- alpha(DATA_restreinte_T2, varphi = 0.1, se = FALSE) 

# Math T3

DATA_essai_T3       <- DATA_2018[ , c(Math_T3)]
DATA_restreinte_T3  <- sample_n(DATA_essai_T3, 50000) # sélectionner les 100 k 
resA_T3_2018        <- alpha(DATA_restreinte_T3, varphi = 0.1, se = FALSE) 



# Math T1

DATA_essai_T1       <- DATA_2019[ , c(Math_T1)]
DATA_restreinte_T1  <- sample_n(DATA_essai_T1, 50000) # sélectionner les 100 k 
resA_T1_2019        <- alpha(DATA_restreinte_T1, varphi = 0.1, se = FALSE) 

# Math T2

DATA_essai_T2       <- DATA_2019[ , c(Math_T2)]
DATA_restreinte_T2  <- sample_n(DATA_essai_T2, 50000) # sélectionner les 100 k 
resA_T2_2019        <- alpha(DATA_restreinte_T2, varphi = 0.1, se = FALSE) 

# Math T3

DATA_essai_T3       <- DATA_2019[ , c(Math_T3)]
DATA_restreinte_T3  <- sample_n(DATA_essai_T3, 50000) # sélectionner les 100 k 
resA_T3_2019        <- alpha(DATA_restreinte_T3, varphi = 0.1, se = FALSE) 



# Math T1

DATA_essai_T1       <- DATA_2020[ , c(Math_T1)]
DATA_restreinte_T1  <- sample_n(DATA_essai_T1, 50000) # sélectionner les 100 k 
resA_T1_2020        <- alpha(DATA_restreinte_T1, varphi = 0.1, se = FALSE) 

# Math T2

DATA_essai_T2       <- DATA_2020[ , c(Math_T2)]
DATA_restreinte_T2  <- sample_n(DATA_essai_T2, 50000) # sélectionner les 100 k 
resA_T2_2020        <- alpha(DATA_restreinte_T2, varphi = 0.1, se = FALSE) 

# Math T3

DATA_essai_T3       <- DATA_2020[ , c(Math_T3)]
DATA_restreinte_T3  <- sample_n(DATA_essai_T3, 50000) # sélectionner les 100 k 
resA_T3_2020        <- alpha(DATA_restreinte_T3, varphi = 0.1, se = FALSE) 



# Math T1

DATA_essai_T1       <- DATA_2021[ , c(Math_T1)]
DATA_restreinte_T1  <- sample_n(DATA_essai_T1, 50000) # sélectionner les 100 k 
resA_T1_2021        <- alpha(DATA_restreinte_T1, varphi = 0.1, se = FALSE) 

# Math T2

DATA_essai_T2       <- DATA_2021[ , c(Math_T2)]
DATA_restreinte_T2  <- sample_n(DATA_essai_T2, 50000) # sélectionner les 100 k 
resA_T2_2021        <- alpha(DATA_restreinte_T2, varphi = 0.1, se = FALSE) 

# Math T3

DATA_essai_T3       <- DATA_2021[ , c(Math_T3)]
DATA_restreinte_T3  <- sample_n(DATA_essai_T3, 50000) # sélectionner les 100 k 
resA_T3_2021        <- alpha(DATA_restreinte_T3, varphi = 0.1, se = FALSE) 

```

### Omega : Pop restreinte

```{r}

# Math T1
resO_T1_2018 <- omega(DATA_restreinte_T1, varphi = 0.1, se = FALSE) 
# Math T2
resO_T2_2018 <- omega(DATA_restreinte_T2, varphi = 0.1, se = FALSE) 
# Math T3
resO_T3_2018 <- omega(DATA_restreinte_T3, varphi = 0.1, se = FALSE)


# Math T1
resO_T1_2019 <- omega(DATA_restreinte_T1, varphi = 0.1, se = FALSE) 
# Math T2
resO_T2_2019 <- omega(DATA_restreinte_T2, varphi = 0.1, se = FALSE) 
# Math T3
resO_T3_2019 <- omega(DATA_restreinte_T3, varphi = 0.1, se = FALSE)


# Math T1
resO_T1_2020 <- omega(DATA_restreinte_T1, varphi = 0.1, se = FALSE) 
# Math T2
resO_T2_2020 <- omega(DATA_restreinte_T2, varphi = 0.1, se = FALSE) 
# Math T3
resO_T3_2020 <- omega(DATA_restreinte_T3, varphi = 0.1, se = FALSE)


# Math T1
resO_T1_2021 <- omega(DATA_restreinte_T1, varphi = 0.1, se = FALSE) 
# Math T2
resO_T2_2021 <- omega(DATA_restreinte_T2, varphi = 0.1, se = FALSE) 
# Math T3
resO_T3_2021 <- omega(DATA_restreinte_T3, varphi = 0.1, se = FALSE)

```
