---
title: "Graph_3_CohensD"
author: "Pauline MARTINOT"
date: "Nov 2023"
output:
  pdf_document: default
  html_document: default
---


# Parameters to set before launch of the pipeline

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(ggplot2)
library(reshape2)
library(alluvial)
library(patchwork)
library(gmodels)
library(rmarkdown)
library(ciTools)
library(rstatix)

library(lmerTest)
library(glmertree)
library(performance)
library(broom)

```


# Ttest and ANOVA on Gau data_n = Table S12 and Table S13

### + Data Gau

```{r}


# load("~/Data/cohort_2018_imputed_joined_n.RData")
load(file = paste0("~/Data/cohort_2018_imputed_ModRegLin_Gau_From_joined_complete_v06112023.RData")) # DATA_AGE_gau_Base_n
DATA_2018 <- DATA_AGE_gau_Base_n[, c("ID_etab_class", "Sexe_Num", "T1_Math", "T2_Math", "T3_Math", "T1_Language", "T2_Language", "T3_Language", "IPS_Etab_CP", "Age_CP", "heterogeneity_T1_Math", "boy_proportion", "First_sexe_in_T1_Math", "Taille_Classe")]
rm(DATA_AGE_gau_Base_n)

#load("~/Data/cohort_2019_imputed_joined_n.RData")
load(file = paste0("~/Data/cohort_2019_imputed_ModRegLin_Gau_From_joined_complete_v06112023.RData")) # DATA_AGE_gau_Base_n
DATA_2019 <- DATA_AGE_gau_Base_n[, c("ID_etab_class", "Sexe_Num","T1_Math", "T2_Math", "T3_Math", "T1_Language", "T2_Language", "T3_Language", "IPS_Etab_CP", "Age_CP", "heterogeneity_T1_Math", "boy_proportion", "First_sexe_in_T1_Math", "Taille_Classe")]
rm(DATA_AGE_gau_Base_n)

#load("~/Data/cohort_2020_imputed_joined_n.RData")
load(file = paste0("~/Data/cohort_2020_imputed_ModRegLin_Gau_From_joined_complete_v06112023.RData")) # DATA_AGE_gau_Base_n
DATA_2020 <- DATA_AGE_gau_Base_n[, c("ID_etab_class", "Sexe_Num","T1_Math", "T2_Math", "T3_Math", "T1_Language", "T2_Language", "T3_Language", "IPS_Etab_CP", "Age_CP", "heterogeneity_T1_Math", "boy_proportion", "First_sexe_in_T1_Math", "Taille_Classe")]
rm(classes, DATA_AGE_gau_Base_30n, DATA_AGE_gau_Base_n, data_depp, joined, Joined_Fin_3, joined30, joined30_n, joined_n,  m1, model1)

#load("~/Data/cohort_2021_imputed_joined_n.RData")
load(file = paste0("~/Data/cohort_2021_imputed_ModRegLin_Gau_From_joined_complete_v06112023.RData")) # DATA_AGE_gau_Base_n
DATA_2021 <- DATA_AGE_gau_Base_n[, c("ID_etab_class", "Sexe_Num","T1_Math", "T2_Math", "T3_Math", "T1_Language", "T2_Language", "T3_Language", "IPS_Etab_CP", "Age_CP", "heterogeneity_T1_Math", "boy_proportion", "First_sexe_in_T1_Math", "Taille_Classe")]
rm(classes, DATA_AGE_gau_Base_30n, DATA_AGE_gau_Base_n, data_depp, joined, Joined_Fin_3, joined30, joined30_n, joined_n)


```

### + Effects of Covid19 (absence of school) between 2018, 2019, 2020 and 2021

```{r}

# 1 base of data with all the 3 millions of children and 1 common variable (e.g., Year)

DATA_2018$Year    <- 2018
DATA_2019$Year    <- 2019
DATA_2020$Year    <- 2020
DATA_2021$Year    <- 2021

DATA_2018$Diff_Math_T3_T2 <- as.numeric(DATA_2018$T3_Math - DATA_2018$T2_Math)
mean(DATA_2018$Diff_Math_T3_T2)
summary(DATA_2018$Diff_Math_T3_T2)
DATA_2018$Diff_Math_T2_T1 <- as.numeric(DATA_2018$T2_Math - DATA_2018$T1_Math)
mean(DATA_2018$Diff_Math_T2_T1)
summary(DATA_2018$Diff_Math_T2_T1)
DATA_2018$Diff_Lang_T3_T2 <- as.numeric(DATA_2018$T3_Language - DATA_2018$T2_Language)
mean(DATA_2018$Diff_Lang_T3_T2)
summary(DATA_2018$Diff_Lang_T3_T2)
DATA_2018$Diff_Lang_T2_T1 <- as.numeric(DATA_2018$T2_Language - DATA_2018$T1_Language)
mean(DATA_2018$Diff_Lang_T2_T1)
summary(DATA_2018$Diff_Lang_T2_T1)

DATA_2019$Diff_Math_T3_T2 <- as.numeric(DATA_2019$T3_Math - DATA_2019$T2_Math)
mean(DATA_2019$Diff_Math_T3_T2)
summary(DATA_2019$Diff_Math_T3_T2)
DATA_2019$Diff_Math_T2_T1 <- as.numeric(DATA_2019$T2_Math - DATA_2019$T1_Math)
mean(DATA_2019$Diff_Math_T2_T1)
summary(DATA_2019$Diff_Math_T2_T1)
DATA_2019$Diff_Lang_T3_T2 <- as.numeric(DATA_2019$T3_Language - DATA_2019$T2_Language)
mean(DATA_2019$Diff_Lang_T3_T2)
summary(DATA_2019$Diff_Lang_T3_T2)
DATA_2019$Diff_Lang_T2_T1 <- as.numeric(DATA_2019$T2_Language - DATA_2019$T1_Language)
mean(DATA_2019$Diff_Lang_T2_T1)
summary(DATA_2019$Diff_Lang_T2_T1)

DATA_2020$Diff_Math_T3_T2 <- as.numeric(DATA_2020$T3_Math - DATA_2020$T2_Math)
mean(DATA_2020$Diff_Math_T3_T2)
summary(DATA_2020$Diff_Math_T3_T2)
DATA_2020$Diff_Math_T2_T1 <- as.numeric(DATA_2020$T2_Math - DATA_2020$T1_Math)
mean(DATA_2020$Diff_Math_T2_T1)
summary(DATA_2020$Diff_Math_T2_T1)
DATA_2020$Diff_Lang_T3_T2 <- as.numeric(DATA_2020$T3_Language - DATA_2020$T2_Language)
mean(DATA_2020$Diff_Lang_T3_T2)
summary(DATA_2020$Diff_Lang_T3_T2)
DATA_2020$Diff_Lang_T2_T1 <- as.numeric(DATA_2020$T2_Language - DATA_2020$T1_Language)
mean(DATA_2020$Diff_Lang_T2_T1)
summary(DATA_2020$Diff_Lang_T2_T1)

DATA_2021$Diff_Math_T3_T2 <- as.numeric(DATA_2021$T3_Math - DATA_2021$T2_Math)
mean(DATA_2021$Diff_Math_T3_T2)
summary(DATA_2021$Diff_Math_T3_T2)
DATA_2021$Diff_Math_T2_T1 <- as.numeric(DATA_2021$T2_Math - DATA_2021$T1_Math)
mean(DATA_2021$Diff_Math_T2_T1)
summary(DATA_2021$Diff_Math_T2_T1)
DATA_2021$Diff_Lang_T3_T2 <- as.numeric(DATA_2021$T3_Language - DATA_2021$T2_Language)
mean(DATA_2021$Diff_Lang_T3_T2)
summary(DATA_2021$Diff_Lang_T3_T2)
DATA_2021$Diff_Lang_T2_T1 <- as.numeric(DATA_2021$T2_Language - DATA_2021$T1_Language)
mean(DATA_2021$Diff_Lang_T2_T1)
summary(DATA_2021$Diff_Lang_T2_T1)

# New common data base

DATA_totale <- rbind(DATA_2018, DATA_2019, DATA_2020, DATA_2021)

### Building the gender gap difference per individual

DATA_totale$Diff_Math_T3_T2 <- as.numeric(DATA_totale$T3_Math - DATA_totale$T2_Math)
DATA_totale$Diff_Math_T2_T1 <- as.numeric(DATA_totale$T2_Math - DATA_totale$T1_Math)
#DATA_totale$Diff_Math_T3_T1 <- as.numeric(DATA_totale$T3_Math - DATA_totale$T1_Math)
DATA_totale$Diff_Lang_T3_T2 <- as.numeric(DATA_totale$T3_Language - DATA_totale$T2_Language)
DATA_totale$Diff_Lang_T2_T1 <- as.numeric(DATA_totale$T2_Language - DATA_totale$T1_Language)
#DATA_totale$Diff_Lang_T3_T1 <- as.numeric(DATA_totale$T3_Language - DATA_totale$T1_Language)

# New common data base

DATA_1819 <- rbind(DATA_2018, DATA_2019)
DATA_1920 <- rbind(DATA_2019, DATA_2020)
DATA_20_21 <- rbind(DATA_2020, DATA_2021)
DATA_1821 <- rbind(DATA_2018, DATA_2021)

DATA_totale$Year  <- as.factor(DATA_totale$Year)
DATA_1819$Year    <- as.factor(DATA_1819$Year)
DATA_1920$Year    <- as.factor(DATA_1920$Year)
DATA_20_21$Year   <- as.factor(DATA_20_21$Year)
DATA_1821$Year    <- as.factor(DATA_1821$Year)

```

### + Cohen s d

We want
(1) Cohen's d or difference of z-score means of gender gaps for Math T2 - Math T1

(2) Cohen's d or ttest for gender gap differences T2-T1 in math in 2019 - 2018 

```{r}

# 2018
# Cohen s d : diff T1-T2 in Math
Data_Cohen <- DATA_2018[, c("Sexe_Boys", "Diff_Math_T2_T1")]
Data_C1 <- Data_Cohen %>%
  group_by(Sexe_Boys) %>%
  cohens_d(Diff_Math_T2_T1 ~ Sexe_Boys, var.equal = FALSE, ref.group = "Boys")
Data_T1 <- Data_C1[, c("Sexe_Boys", "effsize")]

Data_Cohen <- DATA_1819[, c("Sexe_Boys", "Diff_Math_T2_T1", "Year")]


```

### + Fig Cohen s d


```{r}

# Diff T2-T1 Math %>% 2018/2019/2020/2021

DATA_Cohen <- DATA_totale[ , c("Year", "Sexe_Boys", "Diff_Math_T2_T1")]

DATA_C5 <- DATA_Cohen %>%
  group_by(Year) %>%
  cohens_d(Diff_Math_T2_T1 ~ Sexe_Boys, var.equal = FALSE, ref.group = "Boys")
colnames(DATA_C5)[1] <- "Year"
DATA_T1 <- DATA_C5[, c("Sexe_Boys", "effsize", "Year")]

DATA_T1$effsize <- as.numeric(DATA_T1$effsize)
DATA_T1$Year    <- as.factor(DATA_T1$Year) # check if need to transform in as.numeric

legend_title <- "Year"
ggplot(data = DATA_T1, aes(x = Year, y = effsize, color = Year)) +
  geom_smooth(method = "lm", se = TRUE) +
  geom_point(size = 4) +
  geom_hline(yintercept = 0, col = "black") +
  theme_minimal() +
  theme(axis.line.y = element_line(arrow = arrow(length = unit(2, "mm")))) +  
  theme(axis.title.x = element_text(size=9,  color="black", angle=0, hjust = 1)) +
  theme(axis.text.x = element_text(size=9, color="black", angle=0, hjust = 1)) +
  theme(axis.text.y = element_text(size=9, color="black", angle=0, hjust = 1)) +
  ylab("Cohen's D T2-T1 gender gap in math") +
  xlab("Cohort (Year)") +
  #coord_cartesian(ylim=c(-0.014,0.26)) +
  scale_color_manual(legend_title, values=c("deepskyblue", "blue2","midnightblue", "green")) 

ggsave(file = paste0("~/img/", ANNEE_COHORTE, "Graph_Table_S12_", ANNEE_COHORTE, ".svg"), width = 7, height = 5)

```


### + ANOVA

```{r}

# Global model on all years

DATA_totale$Year <- as.factor(DATA_totale$Year)
#DATA_totale$Year <- as.numeric(DATA_totale$Year)

model1 <- lmer(Diff_Math_T3_T2 ~

                 Year +
                 Sexe_Num +
                 Sexe_Num*Year +

                 (1 | ID_etab_class), 
                 data = DATA_totale,  REML = FALSE)


summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/Comparing_Model_18_19_20_21_Modele_Simple_wo_interactions_DiffMathT3_T2_VF.csv"), row.names = F)
rm(model1, m1)

# 2018 - 2019

model1 <- lmer(Diff_Math_T3_T2 ~

                 Year +
                 Sexe_Num +
                 Sexe_Num*Year +

                 (1 | ID_etab_class), 
                 data = DATA_1819,  REML = FALSE)


summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/Comparing_Model_18_19_Modele_Simple_wo_interactions_DiffMathT3_T2_VF.csv"), row.names = F)
rm(model1, m1)

# 2019 - 2020

model1 <- lmer(Diff_Math_T3_T2 ~

                 Year +
                 Sexe_Num +
                 Sexe_Num*Year +

                 (1 | ID_etab_class), 
                 data = DATA_1920,  REML = FALSE)


summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/Comparing_Model_19_20_Modele_Simple_wo_interactions_DiffMathT3_T2_VF.csv"), row.names = F)
rm(model1, m1)

# 2020 - 2021

model1 <- lmer(Diff_Math_T3_T2 ~

                 Year +
                 Sexe_Num +
                 Sexe_Num*Year +

                 (1 | ID_etab_class), 
                 data = DATA_20_21,  REML = FALSE)


summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/Comparing_Model_20_21_Modele_Simple_wo_interactions_DiffMathT3_T2_VF.csv"), row.names = F)
rm(model1, m1)





#DATA_totale$Year <- as.factor(DATA_totale$Year)

model1 <- lmer(Diff_Math_T3_T2 ~

                 Year +
                 #T1_Language +
                 T1_Math +
                 Sexe_Num +
                 IPS_Etab_CP +
                 Age_CP + # Age_CP does not work 
                 heterogeneity_T1_Math +
                 boy_proportion +
                 First_sexe_in_T1_Math +
                 Taille_Classe +
                 
                 Sexe_Num*Year +

                 (1 | ID_etab_class), 
                 data = DATA_totale,  REML = FALSE)


summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/Comparing_Model_18_19_20_21_Modele_Complet_wo_interactions_DiffMathT3_T2_VF.csv"), row.names = F)
rm(model1, m1)

```







# Data 3 Gau ANOVA 

### Latest model ANOVA complexe : without any interactions but gender * year

```{r}

# 2018

load("~/Data/These_Chap4_Data_Gau_2018_Worst_students.RData")
DATA_2018 <- DATA_AGE_gau_Base_n
rm(DATA_AGE_gau_Base_n)

# 2019

load("~/Data/These_Chap4_Data_Gau_2019_Worst_students.RData")
DATA_2019 <- DATA_AGE_gau_Base_n
rm(DATA_AGE_gau_Base_n)

# 2020

load("~/Data/These_Chap4_Data_Gau_2020_Worst_students.RData")
DATA_2020 <- DATA_AGE_gau_Base_n
rm(DATA_AGE_gau_Base_n)

# 2021

load("~/Data/These_Chap4_Data_Gau_2021_Worst_students.RData")
DATA_2021 <- DATA_AGE_gau_Base_n
rm(DATA_AGE_gau_Base_n)


DATA_2018$Year    <- 2018
DATA_2019$Year    <- 2019
DATA_2020$Year    <- 2020
DATA_2021$Year    <- 2021

DATA_2018$Diff_Math_T3_T2 <- as.numeric(DATA_2018$T3_Math - DATA_2018$T2_Math)
DATA_2018$Diff_Math_T2_T1 <- as.numeric(DATA_2018$T2_Math - DATA_2018$T1_Math)
DATA_2018$Diff_Math_T3_T1 <- as.numeric(DATA_2018$T3_Math - DATA_2018$T1_Math)
DATA_2018$Diff_Lang_T3_T2 <- as.numeric(DATA_2018$T3_Language - DATA_2018$T2_Language)
DATA_2018$Diff_Lang_T2_T1 <- as.numeric(DATA_2018$T2_Language - DATA_2018$T1_Language)
DATA_2018$Diff_Lang_T3_T1 <- as.numeric(DATA_2018$T3_Language - DATA_2018$T1_Language)

DATA_2019$Diff_Math_T3_T2 <- as.numeric(DATA_2019$T3_Math - DATA_2019$T2_Math)
DATA_2019$Diff_Math_T2_T1 <- as.numeric(DATA_2019$T2_Math - DATA_2019$T1_Math)
DATA_2019$Diff_Math_T3_T1 <- as.numeric(DATA_2019$T3_Math - DATA_2019$T1_Math)
DATA_2019$Diff_Lang_T3_T2 <- as.numeric(DATA_2019$T3_Language - DATA_2019$T2_Language)
DATA_2019$Diff_Lang_T2_T1 <- as.numeric(DATA_2019$T2_Language - DATA_2019$T1_Language)
DATA_2019$Diff_Lang_T3_T1 <- as.numeric(DATA_2019$T3_Language - DATA_2019$T1_Language)

DATA_2020$Diff_Math_T3_T2 <- as.numeric(DATA_2020$T3_Math - DATA_2020$T2_Math)
DATA_2020$Diff_Math_T2_T1 <- as.numeric(DATA_2020$T2_Math - DATA_2020$T1_Math)
DATA_2020$Diff_Math_T3_T1 <- as.numeric(DATA_2020$T3_Math - DATA_2020$T1_Math)
DATA_2020$Diff_Lang_T3_T2 <- as.numeric(DATA_2020$T3_Language - DATA_2020$T2_Language)
DATA_2020$Diff_Lang_T2_T1 <- as.numeric(DATA_2020$T2_Language - DATA_2020$T1_Language)
DATA_2020$Diff_Lang_T3_T1 <- as.numeric(DATA_2020$T3_Language - DATA_2020$T1_Language)

DATA_2021$Diff_Math_T3_T2 <- as.numeric(DATA_2021$T3_Math - DATA_2021$T2_Math)
DATA_2021$Diff_Math_T2_T1 <- as.numeric(DATA_2021$T2_Math - DATA_2021$T1_Math)
DATA_2021$Diff_Math_T3_T1 <- as.numeric(DATA_2021$T3_Math - DATA_2021$T1_Math)
DATA_2021$Diff_Lang_T3_T2 <- as.numeric(DATA_2021$T3_Language - DATA_2021$T2_Language)
DATA_2021$Diff_Lang_T2_T1 <- as.numeric(DATA_2021$T2_Language - DATA_2021$T1_Language)
DATA_2021$Diff_Lang_T3_T1 <- as.numeric(DATA_2021$T3_Language - DATA_2021$T1_Language)

# New common data base

DATA_totale <- rbind(DATA_2018, DATA_2019, DATA_2020, DATA_2021)

### Building the gender gap difference per individual

DATA_totale$Diff_Math_T3_T2 <- as.numeric(DATA_totale$T3_Math - DATA_totale$T2_Math)
DATA_totale$Diff_Math_T2_T1 <- as.numeric(DATA_totale$T2_Math - DATA_totale$T1_Math)
DATA_totale$Diff_Math_T3_T1 <- as.numeric(DATA_totale$T3_Math - DATA_totale$T1_Math)
DATA_totale$Diff_Lang_T3_T2 <- as.numeric(DATA_totale$T3_Language - DATA_totale$T2_Language)
DATA_totale$Diff_Lang_T2_T1 <- as.numeric(DATA_totale$T2_Language - DATA_totale$T1_Language)
DATA_totale$Diff_Lang_T3_T1 <- as.numeric(DATA_totale$T3_Language - DATA_totale$T1_Language)

# New common data base

DATA_1819 <- rbind(DATA_2018, DATA_2019)
DATA_1920 <- rbind(DATA_2019, DATA_2020)
DATA_20_21 <- rbind(DATA_2020, DATA_2021)
DATA_1821 <- rbind(DATA_2018, DATA_2021)

DATA_totale$Year  <- as.factor(DATA_totale$Year)
DATA_1819$Year    <- as.factor(DATA_1819$Year)
DATA_1920$Year    <- as.factor(DATA_1920$Year)
DATA_20_21$Year   <- as.factor(DATA_20_21$Year)
DATA_1821$Year    <- as.factor(DATA_1821$Year)

```

```{r}

#DATA_totale$Year <- as.factor(DATA_totale$Year)

model1 <- lmer(Diff_Math_T3_T2 ~

                 Year +
                 T1_Language +
                 T1_Math +
                 Sexe_Num +
                 IPS_Etab_CP +
                 Age_CP + # Age_CP does not work 
                 heterogeneity_T1_Math +
                 boy_proportion +
                 First_sexe_in_T1_Math +
                 Taille_Classe +
                 
                 Sexe_Num*Year +

                 (1 | ID_etab_class), 
                 data = DATA_totale,  REML = FALSE)


summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/Comparing_Model_18_19_20_21_Modele_Complet_wo_interactions_DiffMathT3_T2_VF.csv"), row.names = F)
rm(model1, m1)

```

### ANOVA - Linear model of ANOVA

We want to assess the interaction between the year and the gender gap difference between T2 and T1 and between T3 and T2.

Our hypothesis is that the interaction will be positive and significant as the gender gap difference between T3 and T2 is larger in 2018 and 2022, years where children went to school for a longer time compared to the interaction between years and the gender gap difference between T2 and T1 that is similar according to the years. 

We compare the individual difference between T3 - T2 in Math in function of the Year, and the Gender, with an interaction assessed between the Year and the gender (e.g., Year*Gender)

```{r}
# Model comparing Math level and language level between 2018, 2019, 2020 and 2021

# Model Math T1

model1 <- lm(T1_Math ~ Year,
               data = DATA_totale)
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/ANOVA_Data_totale_MathT1.csv"), row.names = F)
rm(model1, m1)


library(rstatix)
Anova_m1 <- anova_test(
  data = DATA_totale,
  T1_Math ~ Year,
  effect.size = "ges")

get_anova_table(Anova_m1, correction = "none")


# Model Math T2

model1 <- lm(T2_Math ~ Year,
               data = DATA_totale)
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/ANOVA_Data_totale_MathT2.csv"), row.names = F)
rm(model1, m1)

# Model Math T3

model1 <- lm(T3_Math ~ Year,
               data = DATA_totale)
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/ANOVA_Data_totale_MathT3.csv"), row.names = F)
rm(model1, m1)

# Model Math T1 years 2018, 2019,  2020, 2021

model1 <- lm(T1_Math ~ Year,
               data = DATA_1819)
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/ANOVA_Data_totale_MathT1_1819.csv"), row.names = F)
rm(model1, m1)

model1 <- lm(T1_Math ~ Year,
               data = DATA_1920)
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/ANOVA_Data_totale_MathT1_1920.csv"), row.names = F)
rm(model1, m1)

model1 <- lm(T1_Math ~ Year,
               data = DATA_20_21)
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/ANOVA_Data_totale_MathT1_20_21.csv"), row.names = F)
rm(model1, m1)

model1 <- lm(T1_Math ~ Year,
               data = DATA_1821)
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/ANOVA_Data_totale_MathT1_1821.csv"), row.names = F)
rm(model1, m1)


# Model Math T2 years 2018, 2019,  2020, 2021

model1 <- lm(T2_Math ~ Year,
               data = DATA_1819)
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/ANOVA_Data_totale_MathT2_1819.csv"), row.names = F)
rm(model1, m1)

model1 <- lm(T2_Math ~ Year,
               data = DATA_1920)
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/ANOVA_Data_totale_MathT2_1920.csv"), row.names = F)
rm(model1, m1)

model1 <- lm(T2_Math ~ Year,
               data = DATA_20_21)
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/ANOVA_Data_totale_MathT2_20_21.csv"), row.names = F)
rm(model1, m1)

model1 <- lm(T2_Math ~ Year,
               data = DATA_1821)
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/ANOVA_Data_totale_MathT2_1821.csv"), row.names = F)
rm(model1, m1)


# Model Math T3 years 2018, 2019,  2020, 2021

model1 <- lm(T3_Math ~ Year,
               data = DATA_1819)
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/ANOVA_Data_totale_MathT3_1819.csv"), row.names = F)
rm(model1, m1)

model1 <- lm(T3_Math ~ Year,
               data = DATA_1920)
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/ANOVA_Data_totale_MathT3_1920.csv"), row.names = F)
rm(model1, m1)

model1 <- lm(T3_Math ~ Year,
               data = DATA_20_21)
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/ANOVA_Data_totale_MathT3_20_21.csv"), row.names = F)
rm(model1, m1)

model1 <- lm(T3_Math ~ Year,
               data = DATA_1821)
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/ANOVA_Data_totale_MathT3_1821.csv"), row.names = F)
rm(model1, m1)



# Model Data totale

model1 <- lm(Diff_Math_T3_T2 ~
                 Year +
                 Sexe_Num +
                 Year*Sexe_Num,
               data = DATA_totale)
               
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/Comparing_Model_2018_2019_2020_2021_Math_T3_T2.csv"), row.names = F)
rm(model1, m1)

Anova_m1 <- anova_test(
  data = DATA_totale,
  Diff_Math_T3_T2 ~ Year + Sexe_Num + Year*Sexe_Num,
  effect.size = "ges")

get_anova_table(Anova_m1, correction = "none")


# Model Data 1819

model1 <- lm(Diff_Math_T3_T2 ~
                 Year +
                 Sexe_Num +
                 Year*Sexe_Num,
               data = DATA_1819)
               
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/Comparing_DATA_1819_Math_T3_T2.csv"), row.names = F)
rm(model1, m1)

# Model Data 1920

model1 <- lm(Diff_Math_T3_T2 ~
                 Year +
                 Sexe_Num +
                 Year*Sexe_Num,
               data = DATA_1920)
               
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/Comparing_DATA_1920_Math_T3_T2.csv"), row.names = F)
rm(model1, m1)

# Model Data 2021

model1 <- lm(Diff_Math_T3_T2 ~
                 Year +
                 Sexe_Num +
                 Year*Sexe_Num,
               data = DATA_20_21)
               
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/Comparing_DATA_2021_Math_T3_T2.csv"), row.names = F)
rm(model1, m1)

# Model Data 1821

model1 <- lm(Diff_Math_T3_T2 ~
                 Year +
                 Sexe_Num +
                 Year*Sexe_Num,
               data = DATA_1821)
               
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/Comparing_DATA_1821_Math_T3_T2.csv"), row.names = F)
rm(model1, m1)



model0 <- lm(Diff_Math_T2_T1 ~ Year , data = DATA_totale)

model2 <- lm(Diff_Math_T2_T1 ~
                 Year +
                 Sexe_Num +
                 Year*Sexe_Num,
               data = DATA_totale)
               
summary(model2)
m2 <- coef(summary(model2))
m2
write.csv2(m2, file= paste0("~/table/Comparing_Model_2018_2019_2020_2021_Math_T2_T1.csv"), row.names = F)
rm(model2, m2, model0)


model0 <- lm(Diff_Math_T3_T1 ~ Year , data = DATA_totale)

model4 <- lm(Diff_Math_T3_T1 ~
                 Year +
                 Sexe_Num +
                 Year*Sexe_Num,
               data = DATA_totale)
               
summary(model4)
m4 <- coef(summary(model4))
m4
write.csv2(m4, file= paste0("~/table/Comparing_Model_2018_2019_2020_2021_Math_T3_T1.csv"), row.names = F)
rm(model4, m4, model0)



model1 <- lm(Diff_Lang_T3_T2 ~
                 Year +
                 Sexe_Num +
                 Year*Sexe_Num,
               data = DATA_totale)
               
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("~/table/Comparing_Model_2018_2019_2020_2021_Lang_T3_T2.csv"), row.names = F)
rm(model1, m1)


model0 <- lm(Diff_Lang_T2_T1 ~ Year , data = DATA_totale)

model2 <- lm(Diff_Lang_T2_T1 ~
                 Year +
                 Sexe_Num +
                 Year*Sexe_Num,
               data = DATA_totale)
               
summary(model2)
m2 <- coef(summary(model2))
m2
write.csv2(m2, file= paste0("~/table/Comparing_Model_2018_2019_2020_2021_Lang_T2_T1.csv"), row.names = F)
rm(model2, m2, model0)



model0 <- lm(Diff_Lang_T3_T1 ~ Year , data = DATA_totale)

model4 <- lm(Diff_Lang_T3_T1 ~
                 Year +
                 Sexe_Num +
                 Year*Sexe_Num,
               data = DATA_totale)
               
summary(model4)
m4 <- coef(summary(model4))
m4
write.csv2(m4, file= paste0("~/table/Comparing_Model_2018_2019_2020_2021_Lang_T3_T1.csv"), row.names = F)
rm(model4, m4, model0)


rm(DATA_2018, DATA_2019, DATA_2020, DATA_2021, DATA_totale)

```



